Roster Review (Generic)

### 2019-05-31 rosterReview_generic.Rmd
Overwrite and inner join fix

```{r}
force <- FALSE
batter_file <- NULL
pitcher_file <- NULL

rosters <- load_players_with_projections(force, batter_file, pitcher_file)
```

```{r}
#TODO move to helper
rosters %>% 
  filter(!type == 'NA', !team == 'Free Agent') %>%
  group_by(type) %>% 
  summarize(adj = median(z_sum)) -> z_sum_adj

>>>>

```{r}
force <- FALSE
force_all <- FALSE
batter_file <- NULL
pitcher_file <- NULL

rosters <- load_players_with_projections(force, force_all, batter_file, pitcher_file)
```

```{r}
#TODO move to helper
rosters %>% 
  filter(type != 'NA', team != 'Free Agent') %>%
  group_by(type) %>% 
  summarize(adj = median(z_sum)) -> z_sum_adj
